---
title: "MWANGE CARLVIN JERRY's CV"
author: Mwange Carlvin Jerry
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ["css/resume.css"]
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1KZ3za7zbPXUITjnWR_f9tvrrtTnce_W1YoSxhqrFkJw/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

<!-- ```{r} -->
<!-- # Build interactive network of positions colored by section -->
<!-- # and connected if they occurred in the same year -->
<!-- datadrivencv::build_network_logo(CV$entries_data) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- if(params$pdf_mode){ -->
<!--   cat("View this CV online with links at _carlvinjerry.me/cv/_") -->
<!-- } else { -->
<!--   cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/CarlvinJerry/Resume/carlvin_cv.pdf)") -->
<!-- } -->
<!-- ``` -->

### CONTACT INFO

- <i class="fa fa-envelope"></i> carlvinjerry@gmail.com

- <i class="fa fa-github"></i> [GitHub: `@`CarlvinJerry](https://github.com/CarlvinJerry)

- <i class="fa fa-linkedin"></i> [LinkedIn](https://www.linkedin.com/in/carlvinmwange/)

- <i class="fa fa-mobile" aria-hidden="true"></i> +254 704942588

- <i class="fa fa-home"></i> [Carlvin || Beyond Raw Data](https://beyondrawdata.rbind.io/)

- For more information, kindly contact me via email.

<!-- <br> -->
<!-- -------------------------------------------------------------------------------- -->

<br>


<!-- ###SKILLZZ -->

<!-- <i class="fab fa-r-project"></i> `R` -->

<!-- <i class="far fa-chart-bar"></i> `tidyverse` -->

<!-- <i class="fas fa-code-branch"></i> `Git` -->

<!-- <i class="fab fa-github"></i> `GitHub` -->

<!-- <i class="fab fa-markdown"></i> `Markdown` -->

<!-- <i class="fab fa-html5"></i> `HTML` -->

<!-- <i class="fab fa-css3-alt"></i> `CSS` -->

<!-- <br><br> -->

<!-- ### LANGUAGE SKILLS -->

<!-- ```{r} -->
<!--  CV %<>% print_skill_bars() -->
<!-- ``` -->

<!-- <br><br> -->

Main
================================================================================

MWANGE CARLVIN JERRY {#title}
--------------------------------------------------------------------------------
<br>

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

<br>

Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

::: aside 

## SKILLS

<i class="fas fa-file-code"></i> `F# - Functional programming`

<i class="fas fa-file-code"></i> `Julia - Numerical Computing`

<i class="fas fa-chart-bar"></i> `Power BI / Tableau`

<i class="fab fa-python"></i> `Python - Data Analysis & ML`

<i class="fab fa-r-project"></i> `R(tidyverse, Shiny) - Data Analysis & ML`

<i class="fas fa-database"></i> `SQL - DBMS`




I have worked in a variety of roles mainly revolving research & development in data analytics. I like collaborative environments where I can learn from my peers. Capable of working well both individually as well as in teams with minimum or no supervision and follow through assignments.

::: 

```{r}
CV %<>% print_section('industry_positions')
```



<!-- These breaks just force a new page so section doesnt get cut off -->
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>


Selected Data Science Writing {data-icon=chart-line}
--------------------------------------------------------------------------------

::: aside

Being an avid data analyst, I challenge myself often to tackle different data analysis & visualization problems.Findings from these challenges are documented on my personal blog.

:::

```{r}
CV %<>% print_section('data_science_writings')
```

<br>


Selected Projects  {data-icon=tasks}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('projects')
```


<br>
<br>


Honors & Awards  {data-icon=trophy}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('honors_and_awards')
```

<br>
<br>
<br>
<br>
<br><br><br>

Referees  {data-icon=users}
--------------------------------------------------------------------------------


George Mbuthia Ndungu,  
Software Engineer,  
Microsoft EA, Kenya,  
Tel: +254 710 773 556,  
Email: v-gendun@microsoft.com  

<br>

Michael Kaboro Maina,  
Engineering Team Lead,  
Innova Limited Kenya,  
Tel: +254 721 205 226,  
Email: michael.kaboro@gmail.com